\documentclass[10pt,a4paper]{article}
\usepackage[margin=1.6cm]{geometry}
\usepackage{paralist}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\renewcommand{\familydefault}{\sfdefault}
\titleformat{\section}{\large\bfseries}{}{0pt}{}
\titleformat{\subsection}{\normalsize\bfseries}{}{0pt}{}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.35em}

\begin{document}

\begin{center}
    {\LARGE\bfseries Caner Kocak}\\[4pt]
    Enschede, Netherlands $\cdot$ \href{tel:+31624990451}{+31 6 2499 0451} $\cdot$ \href{mailto:caner1kocak1@gmail.com}{caner1kocak1@gmail.com}\\[2pt]
    \href{https://www.canerkocak.com}{www.canerkocak.com} $\cdot$ \href{https://github.com/CanerKocak}{github.com/CanerKocak}
\end{center}

\section*{Profile}
Early-career software developer obsessed with learning. I build creative Web3 and AI-driven experiences on the Internet Computer, focus on clean integrations between canisters and external services, and push teams to iterate on shipping practices.

\section*{Skills}
\textbf{Programming languages:} Python, JavaScript, TypeScript, Rust, Motoko, Java, SQL, HTML/CSS\\
\textbf{Blockchain \& Web3:} Internet Computer Protocol, ICRC standards, chain-key cryptography, threshold signatures, Solana SDK\\
\textbf{Frameworks \& tools:} SvelteKit, Vue.js, Flask, Actix-web, WebSockets, WebAssembly SIMD, Git, Docker, Linux, Terraform, AWS\\
\textbf{Data \& testing:} SQLite, PostgreSQL, async I/O, Web2 API integrations, unit testing, API/E2E testing (Cypress)\\
\textbf{Soft skills:} Problem solving, adaptability, independent work, collaboration

\section*{Select projects}
\begin{compactitem}[$\bullet$]
    \item \textbf{Kong Launchpad} --- Full-stack canister factory for proof-of-work token launches. Multi-canister architecture with SIMD-optimized hashing and secure token-gated compute.
    \item \textbf{DittoICP} --- AI-assisted themed drawing dApp on ICP. Architected cascading moderation agents, contest scoring, and tokenized gameplay with Svelte 5 front end and Rust back end.
    \item \textbf{HTTPS Outcall Proxy} --- Rust/Actix-web proxy polling ICP canisters and streaming AI responses from external APIs with TLS, batching, and congestion-aware updates.
    \item \textbf{Windoge98 Suite} --- Browser-based Win98 homage with desktop UI, Microstore marketplace, and Dogvertiser ad builder (SvelteKit, TypeScript, Motoko). Led windowing system, crypto app distribution, and on-chain media storage.
\end{compactitem}

\section*{Experience}
\textbf{Kong (DEX \& Launchpad)} --- Integration \& Backend Developer \hfill 10/2024 -- 08/2025\\[2pt]
Led integrations for a \$5M+ TVL decentralized exchange. Built Solana-to-ICP bridge MVP with threshold Schnorr signatures, extended transaction verification, and delivered Web2 API integrations (CoinMarketCap, CoinGecko, DexTools).\\[4pt]
\textbf{Albert Heijn} --- Store Associate \hfill 06/2017 -- 10/2018\\
Supported daily store operations and customer inquiries with an emphasis on teamwork and reliability.

\section*{Education}
\textbf{Saxion University of Applied Sciences} --- Associate Degree, Software Development \hfill 2021 -- 2024, Enschede \\
\textbf{Saxion University of Applied Sciences} --- Law \hfill 2020 -- 2021, Enschede \\
\textbf{Saxion University of Applied Sciences} --- Industrial Engineering \hfill 2019 -- 2020, Enschede \\
\textbf{Het Assink Lyceum} --- HAVO, Economics \& Society (Anglia Business English, International Business College) \hfill 2017 -- 2019, Haaksbergen \\
\textbf{Het Assink Lyceum} --- VMBO-T, Economics \hfill 2013 -- 2017, Haaksbergen

\section*{Languages}
Dutch (native), English (fluent), Turkish (fluent)

\section*{Growth \& interests}
Unit testing and test automation, C-style languages, React, PHP \& Laravel, ICP blockchain development, Web3, building projects with friends, experimenting with new technologies

\end{document}
